% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{ulem}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Chanyoung Kim}
\hfill{\it\footnotesize Updated \today}}

% --- Contact information and other items ---

\vspace{0.5cm} 
\begin{flushleft}
\begin{tabular}{lll}
% Line 1: Email, GitHub, office location
\textbf{Email}: kochanha@gmail.com      &
\hspace{0.55in} \textbf{GitHub}: github.com/kochanha \\


% Line 2: Phone number, LinkedIn, citizenship
\textbf{Phone}: (+82) 10-2823-5277   & 
\hspace{0.55in} \textbf{LinkedIn}: linkedin.com/in/chanyoung-kim   & 
\end{tabular}
\end{flushleft}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{8pt}

% Set the width of each column
\begin{longtable}{p{1.3in}p{4.8in}}

% --- Section: Research interests ---

\nohyphens{\color{Violet}{Research interests}}
& 3D Computer Vision, Autonomous Flight Drones \\
& \\

% --- Section: Education ---

\color{Violet}{Education} 
& \textbf{Sejong University} \hfill Seoul, Republic of Korea \\ 
& B.S in Intelligence Mechatronics Engineering \hfill Mar. 2017 -- Present \\
& {\it GPA : 3.85 / 4.5}\\
& \\

% --- Uncomment the next few lines if you want to include some courses ---
%& \textbf{Selected coursework}
%\begin{itemize}[noitemsep,leftmargin=*]
%\item \underline{Relevant subject 1}: Course 1, Course 2, Course 3, Course 4
%\item \underline{Relevant subject 2}: Course 1, Course 2, Course 3, Course 4
%\end{itemize} \\



% --- Section: Publications ---
\nohyphens{\color{Violet}{Publications}} 

& \textbf{Performance Evalutaion on Inference 
Time of Ocular Disease Classifier Based on Light Embedded 
Systems} \\
& DongHyun Sim, \uline{\textbf{Chanyoung Kim}}, Suzy Kwak, Jihyun Bae, Woo Jung 
Shin \\
& \textit{The Institute of Electronics and Information Engineers, July. 
2021}\\
%& DOI : \href{https://doi.org/10.1109/CSCI51800.2020.00141}{10.1109/CSCI51800.2020.00141}
& \\


% --- Section: Research experience ---

\nohyphens{\color{Violet}{Research experience}} 
& \textbf{Research Intern, Computer Vision Lab @ Korea University} \\
& {\it Mentor: Prof. Sangpil Kim (Dept. of AI)} \hfill Feb. 2021 -- Present \\
& Research event-based 3D computer vision. Study about event based vision and Artificial Intelligence.
& \\
% --- Section: Teaching experience ---

{\color{Violet}{Teaching experience}} 
& \textbf{Korea National Council on Social Welfare} \\ 
& {\it Mentor} \hfill  Jun. 2020 -- Dec. 2021 \\
& Mentoring IoT, Arduino and Machine Learning to age between 12~14 \\
& \\
& \textbf{LG CNS} \\ 
& {\it Teaching Assistant} \hfill  July. 2021 -- Present \\
& AI Coding Mentoring for LG CNS Executives and Employees\\
& \\


% --- Section: Project experience ---

{\color{Violet}{Project experience}} 
& {\textbf{Seoul Metro}} \\
& {\textbf{Station Attendant Helper Application}} \hfill Jun. 2019 -- Sep. 2019 \\
& {\it Seoul Metro}  \\
& \\

& {\textbf{Ultra-Light Weight TFLite Image Classification Model}} \\
& {\textbf{for Edge Computing Systems}} \hfill Feb. 2021 -- Jun. 2021 \\
& {\it GE Appliances a Haier company}  \\
& \\

& {\textbf{Arial Semantic Segmentation with Drones}} \hfill May. 2021 -- Jun. 2021 \\
& {\it Personal Project} \\
& \\

& {\textbf{Anomaly Detection with Time Series Data}} \hfill Jul. 2021 -- Aug. 2021 \\
& {\it LG CNS} \\
& \\

% --- Section: Awards, scholarships, etc. ---
% --- Note: section title is spread over two lines ---

{\color{Violet}{Awards}} 
& {\textbf{1st Creative Convergence Nomad Idea Competition}} \\
& {\textbf{2nd Prize}} \hfill Dec. 2017 \\
& {\it awarded by the Dean of Software Convergence College, Sejong Univ.}  \\
& Team topic : "Making a Product Using Dye Sensitized Solar Cells(DSSC)"
& \\
& {\textbf{4th Sejong SW Hackathon}} \\
& {\textbf{2nd Prize}} \hfill Jun. 2018 \\
& {\it awarded by Directer of Leading University for Excellence in Software Education Project, Sejong Univ.}  \\
& Team topic : "IoT smart building system for Daeyang AI Center in Sejong Univ."
& \\
& {\textbf{2019 Seoul PM Hackathon}} \\
& {\textbf{5th Prize}} \hfill Jun. 2019 \\
& {\it awarded by Head of the Seoul Institute of Technology.}  \\
& Team topic : "PM Mask Recommendation Depending On Personal State and Estimated Life Shortening Prediction based on AI Model"
& \\
& {\textbf{XXIII Pyeongchang Olympic Winter Games}} \\
& {\textbf{Award of Excellence}} \hfill Feb. 2018 \\
& {\it awarded by President of International Olympic Committee(IOC)}  \\
& {\textbf{Medal of Contribution}} \hfill Jul. 2019 \\
& {\it awarded by Republic of Korea Government Minister of Culture, Sports and Tourism}  \\
& \\
& {\textbf{Seoul Metro}} \\
& {\textbf{Award of Certificate}} \hfill Dec. 2019 \\
& {\it awarded by CEO of Seoul Metro}  \\
& Awarded for App Development Contribution
& \\
& {\textbf{2020 International Robot Contest}} \\
& {\textbf{4th Prize}} \hfill Nov. 2020 \\
& {\it AI Mission Challenge}  \\
& Team topic : "Autonomous Flight Drone"
& \\
& {\textbf{2021 Creative Makers Competition}} \\
& {\textbf{1st Prize}} \hfill Jun. 2021 \\
& {\it awarded by the Dean of Software Convergence College, Sejong Univ.}  \\
& Team topic : "Model Optimization Method for Light Embedded Systems"
&\\
% --- Section: Various skills (programming, software, languages, etc.) ---

\nohyphens{\color{Violet}{Club Activities}}
& \textbf{SMARCLE @ Sejong University} \\
& {\it Vice President} \hfill Sep. 2017 -- Present \\
& I have established an AI club; led a study and various research. \\
& www.smarcle.dev\\
& \\

{\color{Violet}{Skills}} 
& \textbf{Programming}\\
& Proficient in: Python \\
& Familiar with: C++, C \\
& \\
& \textbf{Tools}\\
& Proficient in: MS Office, Tensorflow, Scikit-Learn, Ubuntu, Git \\
& Familiar with: Pytorch, Unity3D, Photoshop \\
& \\
& \textbf{Languages} \\
& Native Speaker in Korean\\
& Proficient in English : 2 years at Mckinley School, Pasadena, CA, USA\\
& Beginer in Japanese\\
% --- Section: Other interests/hobbies ---

% --- End of CV! ---

\end{longtable}
\end{document}